\Large \bf On semidefinite-representable sets over valued fields

### 2025-06-05 article/paper_padic_spec.tex
commit by Simone

Throughout the paper, $K$ refers to a complete,
discrete valued field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
$\OK$ its ring of integers, $\kappa$ its residue field and $\pi$ a uniformizer.
For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
A typical example of $K$ as above is the field of $p$-adic numbers 
$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
have $\OK = \ZZ_p$.
Another example is the field of Laurent series
$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
in which case $\OK = \QQ \llbracket t \rrbracket$.
We refer to \cite{Serre:1979,engler2005valued} for a
general introduction to such fields
and to \cite{caruso_computations_2017}
for an introduction to effective computations over $p$-adic numbers.

>>>>

Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$).
The ring of integers of $K$ is
$$
\OK = \{x \in K : \val(x) \geq 0\},
$$
$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$, and $\pi$ a uniformizer.
For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
A typical example of $K$ as above is the field of $p$-adic numbers 
$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
have $\OK = \ZZ_p$. Another example is the field of Laurent series
$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
in which case $\OK = \QQ \llbracket t \rrbracket$.
We refer to \cite{Serre:1979,engler2005valued} for a
general introduction to such fields
and to \cite{caruso_computations_2017}
for an introduction to effective computations over $p$-adic numbers.
